\documentclass[12pt]{article}
\usepackage[]{blindtext}
\usepackage[letterpaper, total{216mm, 279mm}]{}
\usepackage{amssymb,amsmath,amsfonts,verbatim}
\usepackage[breakable, skins]{tcolorbox}
\usepackage[parfill]{parskip}
\usepackage[english]{babel}
\usepackage{mathtools, amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{verbatim}

\newtheorem{notes}{Notes}[section]
\newtheorem{prob}[notes]{Problems}
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{defn}[notes]{Definition}
\newtheorem{rem}[notes]{Remark}
\newtheorem{prop}[thm]{Proposition}

\newcommand{\rl}{\mathbb{R}}
\newcommand{\id}{\text{id}}
\newcommand{\dprime}{{\prime\prime}}
\newcommand{\xprime}{X^\prime}
\newtcolorbox{mybox}[2][]{
    arc=0mm, enhanced, frame hidden, breakable
}
\newcommand{\qedbox}{$\hfill\blacksquare$}
\newcommand{\mR}{\mathbb{R}}
\newcommand{\mQ}{\mathbb{Q}}
\newcommand{\ds}{\displaystyle}
\newcommand{\al}{\alpha}

\setcounter{MaxMatrixCols}{10}

\pagestyle{empty}
\setlength{\topmargin}{-.65in}
\setlength{\textwidth}{190mm} 
\setlength{\textheight}{240mm}
\setlength{\oddsidemargin}{-15mm} 
\setlength{\evensidemargin}{-15mm}
\parindent=0pt

\title{\textbf{Analysis I} \\
\large Homework 2
}
\author{Nutan Nepal}
\newcommand{\packpledge}{
    $\text{{\bf Pack Pledge:} I have neither given nor
    received unauthorized aid on this
    test or assignment.}$}

\begin{document}
\maketitle
\packpledge\\
\makebox[\linewidth]{\rule{200mm}{1pt}}
\vspace{1mm}

\begin{enumerate}

\item Let $(X, \rho)$ and $(Y, \sigma)$ be metric spaces,
    and let $f: (X, \rho) \to (Y, \sigma)$ be a map
    such that $f^{-1}(V)$ is open in $X$, for all
    $V$ open in $Y$. Show that $f$ is continuous on $X$. 

\begin{mybox}

    \vspace*{15mm}
\end{mybox}


\item ({\bf Continuous mapping}) Show that a
    mapping $T: X\to Y$ is continuous
    if and only if the inverse image of any closed
    set $M\subset Y$ is a closed
    set in $X$.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
 
\item Assume that $f : (\mR^2, d_1 =  \
    \text{Euclidean metric}) \to \mR$ is continuous at
    $x \in \mR^2$. Show that
    $f : (\mR^2, d_2 =  \ \text{taxicab metric})
    \to \mR$ is also continuous at $x$.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}

\item Show that the discrete metric space $(X,d)$ is
    separable iff $X$ is countable. 
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Show that $l^p$, with $1 \leq p <
    \infty$ is separable.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Show that $l^{\infty}$ is not separable.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Let $\{x_n\}_{n \geq 1}$ be a sequence in a m.s.
    $(X, d)$ which converges to $x$. Show that
    $\{x_n\}_{n \geq 1}$ is a bounded sequence.
    Then let $\{y_n\}_{n \geq 1}$ be a sequence in
    $(X, d)$ which converges to $y$. Show that
    $\lim_{n \to \infty} d(x_n, y_n) = d(x,y)$. 
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Show that any nonempty set $A\subset (X, d)$
    is open if and only if it is a
    union of open balls.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}


\item Let $(X, \rho)$ be a metric space, $E \subset X$, and $x \in X$. Prove that the following are equivalent:
\begin{enumerate}
\item $x \in \overline{E}$
\item $B(x,r) \cap E \neq \emptyset$, $\forall r > 0$
\item $\exists \ \{x_n\} \in E$ s.t. $x_n \to x$
\end{enumerate}  
\begin{mybox}

    \vspace*{15mm}
\end{mybox}

 
\item If $d_1$ and $d_2$ are metrics on the same set
    $X$ and there are positive
    numbers $a$ and $b$ such that for all $x$, $y\in X$,
    $$ad_1(x, y)\leq d_2(x,y)\leq bd_1(x,y),$$
    show that the Cauchy sequences in $(X,d_1)$
    and $(X,d_2)$ are the same.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Show that $l^p$, with $1 \leq p < \infty$ is
    complete.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Prove that $(\mR, d(x,y) = |x-y|)$ is complete.\\ 
    Hint: Follow the steps provided in class.
    You can use Bolzano-Weierstrass Theorem without
    proving it.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Prove that $(\mQ, d(x,y) = |x-y|)$ is incomplete.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Prove that $\Big(\text{C}[-1,1], d(f,g) =
    \int_{-1}^1|f(t) - g(t)| \ dt\Big)$ is incomplete. \\
    Hint: Follow the steps provided in class.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Determine whether or not the discrete metric
    space is complete. Justify your answer.
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
\item Prove the Completion of a Metric Space Theorem. 
\begin{mybox}

    \vspace*{15mm}
\end{mybox}
 
 
\end{enumerate}
\end{document}